%==============================================================================
% Appendix D: Auxiliary delta-sector Null Theorem
%==============================================================================
\section{Auxiliary $\delta$-Sector Null Theorem}
\label{app:D}

This appendix gives the detailed proof of Theorem~3 ($\delta$-sector null
theorem).  The objective is to show rigorously that while new $\alpha$-cubics
appear in the physical $(\eta,V)$ channel through the EC extension, no new
homogeneous cubic channel appears in the auxiliary MIXING variable $\delta_k$.

\subsection{Definition}
\label{app:D:def}

For the formal MIXING sector of the unified engine, we define
\begin{equation}
  C_\delta(M^3;\text{mode}) :=
  \left.\frac{\partial^3\Veff}{\partial\delta_0\,\partial\delta_1\,\partial\delta_2}
  \right|_{\delta_0=\delta_1=\delta_2=0},
\end{equation}
where $M^3 = \Sthree, \Tthree, \Nilthree$ and mode $=$ AX/VT/MX.

The two propositions we verify are:
\begin{equation}
  C_\delta = 0,
  \qquad
  \frac{\partial C_\delta}{\partial\alpha} = 0.
\end{equation}
The latter follows immediately from the former, but it is verified independently
in the scripts.

\subsection{$\Sthree\times\Sone$: Exact Zero}
\label{app:D:s3}

The formal MIXING sector can be introduced non-trivially for $\Sthree$.
Therefore, if an auxiliary cubic channel exists, this topology is the most
likely place to find it.

By SymPy direct computation, for each of the AX/VT/MX backgrounds:
\begin{equation}
  \left.\frac{\partial^3\Veff^{S^3}}{\partial\delta_0\,\partial\delta_1\,\partial\delta_2}
  \right|_{\delta=0} = 0.
\end{equation}
Consequently:
\begin{equation}
  \frac{\partial C_\delta(\Sthree)}{\partial\alpha} = 0.
\end{equation}

This result contrasts with \S\ref{sec:s3:ec}:
\begin{equation}
  \frac{\partial^3\Veff}{\partial\alpha\,\partial\eta\,\partial V}
  = -\frac{128\pi^2 V\eta r}{3} \neq 0.
\end{equation}
The new cubic structure activated by the EC extension is confined to the physical
$\eta$-$V$ channel and does not appear in the auxiliary $\delta$-sector.

\subsection{$\Tthree\times\Sone$: Exact Zero}
\label{app:D:t3}

The flatness $C^a_{bc}=0$ trivialises most of the mode dictionary of $\Tthree$.
Even for the formal MIXING sector, the same holds:
\begin{equation}
  \left.\frac{\partial^3\Veff^{T^3}}{\partial\delta_0\,\partial\delta_1\,\partial\delta_2}
  \right|_{\delta=0} = 0
  \quad \text{(all AX/VT/MX backgrounds)}.
\end{equation}
Consequently:
\begin{equation}
  \frac{\partial C_\delta(\Tthree)}{\partial\alpha} = 0.
\end{equation}
In $\Tthree$, neither the physical sector nor the auxiliary sector develops
EC-derived new homogeneous cubic channels.

\subsection{$\Nilthree\times\Sone$: Exact Zero}
\label{app:D:nil3}

$\Nilthree$ has non-zero background Weyl and generates EC false vacua and
spin-2/spin-1 directional splitting.  Nevertheless, for the formal MIXING sector:
\begin{equation}
  \left.\frac{\partial^3\Veff^{Nil^3}}{\partial\delta_0\,\partial\delta_1\,\partial\delta_2}
  \right|_{\delta=0} = 0
  \quad \text{(all AX/VT/MX backgrounds)}.
\end{equation}
Consequently:
\begin{equation}
  \frac{\partial C_\delta(\Nilthree)}{\partial\alpha} = 0.
\end{equation}
The EC-specific physics of $\Nilthree$ (false vacuum, quintet splitting) appears
in the background Weyl and the $(r,\eta,V)$ sector, not as a new auxiliary
$\delta$-sector cubic channel.

\subsection{Summary of All Nine Cases}
\label{app:D:summary}

\begin{table}[H]
\centering
\begin{tabular}{lcccc}
\toprule
Topology & AX & VT & MX & $\partial_\alpha C_\delta$ \\
\midrule
$\Sthree\times\Sone$ & $0$ & $0$ & $0$ & $0$ \\
$\Tthree\times\Sone$ & $0$ & $0$ & $0$ & $0$ \\
$\Nilthree\times\Sone$ & $0$ & $0$ & $0$ & $0$ \\
\bottomrule
\end{tabular}
\caption{All nine cases of the auxiliary cubic coefficient $C_\delta$.  All
  entries are exact zero.}
\label{tab:appD}
\end{table}

The above shows that the auxiliary cubic coefficient defined for the formal
MIXING sector vanishes exactly in all three topologies, and the new homogeneous
cubic structure of the EC extension is confined to the physical $\eta$-$V$
channel.

Script: \texttt{proofs/c\_delta\_null\_proof.py}.
