%==============================================================================
% Homogeneous Three-Topology Comparison and Mode Dictionary
% in Einstein-Cartan + Nieh-Yan Theory: Geometric Structure of EC-Weyl Coupling
%==============================================================================
\documentclass[12pt,a4paper]{article}

%------------------------------------------------------------------------------
% Packages
%------------------------------------------------------------------------------

% Fonts / encoding
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{textcomp}
\usepackage[final]{microtype}

% Math
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{mathtools}
\usepackage{bm}

% Graphics and figures
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}

% Tables
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multirow}

% TikZ for diagrams
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, calc, fit, backgrounds}

% Layout and formatting
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\onehalfspacing

% Misc (xcolor before hyperref)
\usepackage{xcolor}
\usepackage{enumitem}

% References and links
\definecolor{linkblue}{RGB}{0,0,180}
\usepackage[colorlinks=true,linkcolor=linkblue,citecolor=linkblue,urlcolor=linkblue]{hyperref}
\usepackage{cleveref}

% Code listings (for appendices)
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  language=Python
}

% Section break
\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}

%------------------------------------------------------------------------------
% Theorem environments
%------------------------------------------------------------------------------
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

%------------------------------------------------------------------------------
% Custom commands
%------------------------------------------------------------------------------
% Math shortcuts
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Veff}{V_{\mathrm{eff}}}
\newcommand{\VEC}{V_{\mathrm{EC}}}
\newcommand{\LC}{\mathrm{LC}}
\newcommand{\EC}{\mathrm{EC}}
\newcommand{\NY}{\mathrm{NY}}
\newcommand{\Vol}{\mathrm{Vol}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\Sym}{\mathrm{Sym}}

% Topology notation
\newcommand{\Sthree}{S^3}
\newcommand{\Tthree}{T^3}
\newcommand{\Nilthree}{\mathrm{Nil}^3}
\newcommand{\Sone}{S^1}

% Inner product notation
\newcommand{\innerprod}[2]{\langle #1,\, #2 \rangle}

% Spin labels
\newcommand{\phys}{\mathrm{phys}}

%------------------------------------------------------------------------------
% Title and author
%------------------------------------------------------------------------------
\title{Homogeneous Three--Topology Comparison and Mode Dictionary in Einstein--Cartan + Nieh--Yan Theory: Geometric Structure of EC--Weyl Coupling}

\author{Muacca}

\date{}

%==============================================================================
\begin{document}
%==============================================================================

\maketitle
\begin{center}
Version: v1\\
First release: 2026-04-06\\
\end{center}

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
\begin{abstract}
We systematically analyse the homogeneous minisuperspace of gravity with
Einstein--Cartan (EC) connection and Weyl-squared coupling $\alpha C^2_\EC$
across three spatial topologies---$\Sthree\times\Sone$, $\Tthree\times\Sone$,
and $\Nilthree\times\Sone$---and determine how the EC--Weyl coupling modifies
the mode dictionary of each topology.  Extending the Levi--Civita framework of
papers~I--III to the EC connection $\omega_\EC = \Gamma_\LC + K$ (with $K$ the
contortion), we classify torsion modes as axial-scalar (AX), vector-trace (VT),
and their product (MX), and establish nine theorems.

\textbf{Theorem~1 (AX/VT dropout):}  In all three topologies,
$C^2_\EC = C^2_\LC$ holds exactly in the AX ($V=0$) and VT ($\eta=0$)
backgrounds; the EC correction appears only in the MX background as
$C^2_\EC = C^2_\LC + 16V^2\eta^2/(3r^2)$.

\textbf{Theorem~2 (Palatini protection, EC):}  $G^{\EC}_{\eta\eta} =
G^{\EC}_{VV} = 0$ holds algebraically; torsion remains non-propagating
and the spin-2 kinetic structure is unchanged from the LC case.

\textbf{Theorem~3 ($\delta$-sector null theorem):}  The auxiliary cubic
coefficient $C_\delta := \partial^3\Veff/\partial\delta_0\partial\delta_1
\partial\delta_2|_{\delta=0}$ vanishes exactly in all three topologies and all
torsion backgrounds, and $\partial_\alpha C_\delta = 0$.

\textbf{Theorem~4 (Palatini universality):}  In $\Sthree\times\Sone$ the AX
and VT spin-2/spin-1 mass spectra are identical: spin-2 mass
$\mu^2 = 128\pi^2 Lr/(3\kappa^2) - 16384\pi^2 L\alpha/(3r)$ (five-fold
degenerate) and spin-1 mass $m^2_\omega = 16\pi^2 L^3/(\kappa^2 r)$
(three-fold degenerate).

\textbf{Theorem~5 (torsion--volume coupling):}  In $\Tthree\times\Sone$,
$\partial^2\Veff/\partial\varepsilon\partial s|_0 = 48\pi^4 L\eta^2r/\kappa^2
\neq 0$; the cross-term is of purely kinematic origin, independent of the Weyl
mass.

\textbf{Theorem~6 ($\Nilthree$ EC false vacuum):}  For $\alpha<0$,
$\Nilthree\times\Sone$ supports a positive false vacuum at
$r_0 = (4\kappa/\!\sqrt{3})\sqrt{|\alpha|}$ on the $\eta=V=0$ section, with
scaling exponent $\gamma=1/2$.

\textbf{Theorem~7 ($\Nilthree$ quintet splitting):}  The spin-2 quintet around
the EC false vacuum splits as $5\to 0+2+1+1$; the zero mode $q_3$ is
geometrically protected by the one-dimensional Lie structure of $\Nilthree$.

\textbf{Theorem~8 (uniaxial mass splitting):}  In the $\Nilthree$ spin-1
sector, $m^2(\omega_2)\neq 0$ (non-commutative direction) while
$m^2(\omega_0)=m^2(\omega_1)=0$ (commutative directions).

\textbf{Theorem~9 ($\varepsilon$-$s$ cross-term classification):}  The origin
of $\partial^2\Veff/\partial\varepsilon\partial s$ differs essentially across
topologies: purely kinematic for $\Tthree$, vanishing for $\Sthree$, and of
pure curvature/Weyl origin for $\Nilthree$.

These results establish a closed comparison framework for the homogeneous bulk
geometric sector in EC+NY theory under the axial+vector-trace torsion ansatz.
\end{abstract}

%------------------------------------------------------------------------------
% Main text
%------------------------------------------------------------------------------
\input{sections/sec01}   % Introduction
\input{sections/sec02}   % EC-Weyl Coupling Structure
\input{sections/sec03}   % Mode Dictionary: S3 x S1
\input{sections/sec04}   % Mode Dictionary: T3 x S1
\input{sections/sec05}   % Mode Dictionary: Nil3 x S1
\input{sections/sec06}   % Three-Topology Comparison
\input{sections/sec07}   % Physical Interpretation and Outlook
\input{sections/sec08}   % Conclusion

%------------------------------------------------------------------------------
% Acknowledgments
%------------------------------------------------------------------------------
\section*{Acknowledgments}

The author acknowledges the use of the following AI tools during manuscript
preparation: Claude Opus~4.6 (Anthropic; accessed 2026-03),
Gemini~3.1 Pro (Google; accessed 2026-03), Grok 4.2 (xAI; accessed 2026-03),
and GPT-5.4 Thinking via ChatGPT (OpenAI; accessed 2026-03).
These tools were used for language editing (including Japanese--English
translation), outlining and improving exposition, drafting and reviewing
auxiliary code (scripts and pseudocode) that was subsequently tested and
validated by the author, and proposing candidate consistency checks and
alternative derivations to be independently verified by the author.

The AI tools did not determine the scientific claims of this work and were not
used to generate or modify research data or evidentiary figures.  The author
takes full responsibility for the content and for any remaining errors.

This work was developed within the informal collaborative project
\textbf{DPPU} (\textbf{D}onut-like topology, \textbf{P}lanck-scale
compactness, \textbf{P}recession dynamics, \textbf{U}niverse).

%------------------------------------------------------------------------------
% Availability and Contact
%------------------------------------------------------------------------------
\section*{Availability and Contact}

\paragraph{Code and Data Availability}
The code and supplemental data associated with this work are available at:

\begin{itemize}
  \item Zenodo: \texttt{10.5281/zenodo.19425147}
  \item GitHub: \texttt{https://github.com/Muacca/DPPUv2-paper03ec}
\end{itemize}

They are released under the MIT License.

\paragraph{Citation}
If you use these materials, please cite the associated manuscript and Zenodo record:

\begin{quote}
\small
Muacca, ``Homogeneous Three--Topology Comparison and Mode Dictionary \\
in Einstein--Cartan + Nieh--Yan Theory: Geometric Structure of EC--Weyl Coupling.''
\end{quote}

\paragraph{Contact}
For questions, bug reports, or collaboration inquiries:

\begin{itemize}
  \item Email: \texttt{muacca@dmwp.jp}
  \item GitHub Issues: \texttt{https://github.com/Muacca/DPPUv2-paper03ec/issues}
\end{itemize}

%------------------------------------------------------------------------------
% Appendices
%------------------------------------------------------------------------------
\appendix
\input{appendices/appA}  % Notation and Conventions
\input{appendices/appB}  % Complete EFT Coefficient List
\input{appendices/appC}  % Detailed Derivation of eps-s Cross-term
\input{appendices/appD}  % Auxiliary delta-sector Null Theorem

%------------------------------------------------------------------------------
% References
%------------------------------------------------------------------------------
\bibliographystyle{unsrt}

\begin{thebibliography}{99}

\bibitem{paper1}
Muacca,
``Topology-Dependent Phase Classification of Effective Potentials
in Einstein--Cartan + Nieh--Yan Minisuperspace,''
Zenodo.\ \texttt{10.5281/zenodo.18213677} (2026).

\bibitem{paper2}
Muacca,
``Structural Robustness of Isotropic $S^3$ Vacua in Einstein--Cartan
Minisuperspace via Chiral Equilibrium and Weyl Stability,''
Zenodo.\ \texttt{10.5281/zenodo.18815498} (2026).

\bibitem{paper3}
Muacca,
``Unified Geometric Landau EFT of Homogeneous $\Sthree\times\Sone$
Minisuperspace in Einstein--Cartan + Nieh--Yan Theory,''
Zenodo.\ \texttt{10.5281/zenodo.19144481} (2026).

\bibitem{Hehl1976}
F.~W.~Hehl, P.~von der Heyde, G.~D.~Kerlick, and J.~M.~Nester,
``General relativity with spin and torsion: Foundations and prospects,''
Rev.\ Mod.\ Phys.\ \textbf{48}, 393--416 (1976).

\bibitem{NiehYan1982}
H.~T.~Nieh and M.~L.~Yan,
``An identity in Riemann--Cartan geometry,''
J.\ Math.\ Phys.\ \textbf{23}, 373--374 (1982).

\bibitem{Chandia1997}
O.~Chandia and J.~Zanelli,
``Topological invariants, instantons, and the chiral anomaly on spaces
with torsion,''
Phys.\ Rev.\ D \textbf{55}, 7580--7585 (1997).

\bibitem{Woodard2015}
R.~P.~Woodard,
``Ostrogradsky's theorem on Hamiltonian instability,''
Scholarpedia \textbf{10}(8), 32243 (2015).

\end{thebibliography}

%==============================================================================
\end{document}
%==============================================================================
